SMT-Based Generation of Symbolic Automata \thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-11-05 2017-Xudong-SMT/ActaInformatica.tex
Acta Inf. paper: Improve the beginning of Sect.4.3.

\paragraph{Matching.}
The \emph{Matching} method builds the OTs of a pNet node from those of
its subnets.
For each synchronisation vector and each possible
combination of behaviours of the subnets, as generated by the \emph
{Combining} method, it builds the corresponding open transition.
Here, we only detail the construction of the predicate.
Suppose that $sv = \left((a'_i)^{i\in I} (b'_j)^{j\in J}\rightarrow v'\right) \in SV$ is a synchronisation vector, $G_k$ is its guard, and
$c = ({ot}_i)^{i \in [1,n]} \in \overline{comb}$ is a tuple of open transitions such that, for each $i \in [1,n]$, either $ot_i = -$, or the result action of $ot_i$ is $a_i$. Suppose further that $\mathit{hole} = (b_j)^{j \in J}$ is the hole behaviour and $v$ is a fresh variable, representing the result action of the OT under construction. Then we can  build the predicate:
%
\begin{multline*}
  \mathit{MkPred}(sv, c, \overline{\mathit{hole}}, v) = 
  (\forall i\in I, a_i=a'_i) \land
%  (\forall i \not\in I, ot_i = -) \land
  (\forall j\in J, b_j=b'_j) \land
  (v=v') \land G_k.
\end{multline*}

@@

The set $L1$ may contain unreachable transitions. To remove those
transitions, the last step of the  
algorithm (lines 12-14) builds the final open automaton via a traversal of $L1$,
starting at the initial state $InitState(p)$ as defined in
page~\pageref{def-states}. More precisely, this is a residual
algorithm building a graph from the reachable transitions in $L1$. 
%and states are the set of target states of the transitions. 
Each state in the graph is decorated with a set of its local
variables, and a list of their possible assignments,
gathered during the traversal using the ``Post'' parts of the
OTs.

@@

In practice, this could be
expensive, and it is not incorrect to leave some UNSAT OTs in the
result. From a  practical point of view, very little will be gained to compute the
fixed point, so we would only perform one step of iteration. Further algorithms 
(e.g. model-checking or equivalence checking) will be able to use the
full information from the predicates and the assignment sets, even if
some spurious OTs are left here.

>>>>

\paragraph{Matching.}
The \emph{Matching} method builds the OTs of a pNet node from those of
its subnets.
For each synchronisation vector and each possible
combination of behaviours of the subnets, as generated by the \emph
{Combining} method, it builds the corresponding open transition.
Here, we only detail the construction of the predicate.
Suppose that $sv = \left((a'_i)^{i\in I} (b'_j)^{j\in J}\rightarrow v'\right) \in SV$ is a synchronisation vector, $G_k$ is its guard, and
$comb = ({ot}_i)^{i \in [1,n]} \in \overline{comb}$ is a tuple of open transitions such that, for each $i \in [1,n]$, either $ot_i = -$, or the result action of $ot_i$ is $a_i$. Suppose further that $\mathit{hole} = (b_j)^{j \in J}$ is the hole behaviour and $v$ is a fresh variable, representing the result action of the OT under construction. Then we can  build the predicate:
%
\begin{multline*}
  \mathit{MkPred}(sv, comb, \overline{\mathit{hole}}, v) = 
  (\forall i\in I, a_i=a'_i) \land
%  (\forall i \not\in I, ot_i = -) \land
  (\forall j\in J, b_j=b'_j) \land
  (v=v') \land G_k.
\end{multline*}

@@

\QIN{As the removal of the unsatisfiable transitions leads to some transitions losing their pioneer transitions, }
the set $L1$ may contain unreachable transitions. To remove those transitions, the last step of the  
algorithm (lines 12-14) builds the final open automaton via a traversal of $L1$,
starting at the initial state $InitState(p)$ as defined in
page~\pageref{def-states}. More precisely, this is a residual
algorithm building a graph from the reachable transitions in $L1$. 
%and states are the set of target states of the transitions. 
Each state in the graph is decorated with a set of its local
variables, and a list of their possible assignments,
gathered during the traversal using the ``Post'' parts of the
OTs.

@@

In practice, this could be
expensive \QIN{as it needs several times of traversal of the whole set of open transitions}, and it is not incorrect to leave some UNSAT OTs in the
result. \QIN{From a  practical point of view, the unreachable transitions is usually a small part of result open transitions, very little will be gained to compute the fixed point. So we would only perform one step of iteration.} Further algorithms 
(e.g. model-checking or equivalence checking) will be able to use the
full information from the predicates and the assignment sets, even if
some spurious OTs are left here.
